My title

### 2024-10-31 paper/paper.qmd
citations and sites added to paper and update to .bib file

# Results
## Model Output
Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html). This summary reveals the effects of different polling methods and organizations on our estimates. For instance, there is a small difference in estimates between data collected via online panels and phone surveys. The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases. Specifically, variance parameters for different methods (such as online ads vs. phone surveys) indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.

@@

### Defects of Existing Data {#sec-first-point}
Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data. This scarcity of data can make the model highly sensitive to choices in priors and interstate covariance structures. For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment. This issue is also seen across different polling organizations and survey methods. As Gelman et al. (2020) noted, the model can fluctuate between overconfidence and unreasonable uncertainty. To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas. However, these sources carry their own issues, as they may lack reliability and rigor.

Then, in handling systematic bias introduced by different polling methods, the model accounts for variance by assigning specific variance parameters for each method (e.g., phone interviews vs. online panels). Each method may systematically overestimate or underestimate support for a particular candidate【cite】. For instance, online panels may attract more politically engaged individuals, leading to biases compared to random phone interviews. To reduce these biases, the model includes variance adjustments specific to each method. Further improvements could involve re-weighting polls based on historical accuracy or introducing dynamic adjustments for newer polling methods. However, as pointed out in 【2014】, historical data often include responses to unique events that are not repeatable, making it difficult to assess the accuracy of historical information as a reference. Similarly, the model uses a random walk prior to accommodate fluctuations in public support over time, yet it may struggle to capture abrupt changes driven by political events, such as a debate or controversial statement. The inherent randomness of world events makes it challenging to fully address this problem.

@@

### The Influence of Reality
#### Bias and Transparency
The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus. Every polling agency's choices—whether intentional or unintentional—can introduce biases into results. In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases. For example, research from the Pew Research Center and Stanford University shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (source1).

Another complex issue is "partisan nonresponse bias," where certain political groups are less likely to participate in polls. This trend has become more prominent in recent years, notably affecting conservative respondents. Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (source2).

@@

According to a Pew Research Center report, polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups. These groups often require different recruitment strategies and data collection methods, increasing polling costs (Pew Research Center, 2024)【387†source】. Another Pew report highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques【388†source】.

@@

#### The Randomness of the Real World
Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions. Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts. The Harvard Data Science Review highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions[HARVARD DATA SCIENCE REVIEW]

>>>>

# Results
## Model Output
Our results are summarized in a table which is available [here](https://8360846bf92342d59862bf4ec3515643.app.posit.cloud/file_show?path=%2Fcloud%2Fproject%2Fpaper%2Fmodel_summary_table.html). This summary reveals the effects of different polling methods and organizations on our estimates. For instance, there is a small difference in estimates between data collected via online panels and phone surveys. The model adjusts for these differences by using a hierarchical structure, which accounts for inconsistencies caused by methodological and organizational biases. Specifically, variance parameters for different methods indicate the different impacts these methods have on sampling coverage and voter behavior, helping the model balance these differences.

@@

### Defects of Existing Data {#sec-first-point}
Firstly, a major challenge for the model lies in estimating a large number of parameters with limited polling data. This scarcity of data can make the model highly sensitive to choices in priors and interstate covariance structures. For example, relying on historical patterns from states with limited data may fail to reflect the latest shifts in voter sentiment. This issue is also seen across different polling organizations and survey methods. As @gelman2020regression noted, the model can fluctuate between overconfidence and unreasonable uncertainty. To address this, we could consider incorporating alternative data sources, such as social media sentiment or historical population voting trends, to supplement polling data in underrepresented areas. However, these sources carry their own issues, as they may lack reliability and rigor.

Then, in handling systematic bias introduced by different polling methods, the model accounts for variance by assigning specific variance parameters for each method (e.g., phone interviews vs. online panels). Each method may systematically overestimate or underestimate support for a particular candidate. For instance, online panels may attract more politically engaged individuals, leading to biases compared to random phone interviews. To reduce these biases, the model includes variance adjustments specific to each method. Further improvements could involve re-weighting polls based on historical accuracy or introducing dynamic adjustments for newer polling methods. However, as pointed out in @blumenthal2010polls, historical data often include responses to unique events that are not repeatable, making it difficult to assess the accuracy of historical information as a reference. Similarly, the model uses a random walk prior to accommodate fluctuations in public support over time, yet it may struggle to capture abrupt changes driven by political events, such as a debate or controversial statement. The inherent randomness of world events makes it challenging to fully address this problem.

@@

### The Influence of Reality
#### Bias and Transparency
The influence of polling agencies’ biases and methodological transparency on election predictions has long been a research focus. Every polling agency's choices—whether intentional or unintentional—can introduce biases into results. In highly polarized political environments, factors like question wording, sampling techniques, and demographic weighting can amplify potential biases. For example, research from the [Pew Research](https://www.pewresearch.org/short-reads/2024/08/28/key-things-to-know-about-us-election-polling-in-2024/) Center and [Stanford University](https://news.stanford.edu/stories/2020/10/9-things-know-election-polling-data) shows that differences in methods, such as educational weighting or nonresponse adjustments, can lead to significant polling biases, especially for politically sensitive figures like Donald Trump (see @pew2024electionpolling and @stanford2020electionpolling).

Another complex issue is "partisan nonresponse bias," where certain political groups are less likely to participate in polls. This trend has become more prominent in recent years, notably affecting conservative respondents. Pollsters must take extra care in sampling to accurately represent all population segments, which presents particular challenges in practice and makes it hard to eliminate these biases entirely (see @pew2024electionpolling).

@@

According to a [Pew Research Center report](https://www.pewresearch.org/methods/2021/04/08/confronting-2016-and-2020-polling-limitations/), polling biases often stem from financial constraints and methodological choices, such as the use of cost-effective online panels, which may not effectively capture perspectives from older, rural, or technologically less-adept groups. These groups often require different recruitment strategies and data collection methods, increasing polling costs (see @pew2021pollinglimitations). Another [Pew report](https://www.pewresearch.org/politics/2024/09/09/issues-and-the-2024-election/) highlights that participation in extreme partisan regions is often low, which makes balanced representation more challenging and increases the financial and logistical burden of implementing corrective weighting and sampling techniques (see @pew2024issues).

@@

#### The Randomness of the Real World
Voter preferences can shift rapidly due to events like debates, economic changes, or international incidents, challenging election predictions. Regular polling may fail to capture these shifts if not updated frequently, leading to outdated and potentially misleading forecasts. The [Harvard Data Science Review](https://hdsr.mitpress.mit.edu/pub/nw1dzd02/release/2) highlighted this uncertainty in the 2020 election, where state-level opinion volatility was influenced by economic and educational factors, necessitating models that incorporate these dynamic interactions (@gelman2020regression).
